\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-04 bare_conf.tex
typo fixed.
bibliography fixed.

More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes a high level architecture of the proposed technology aid for visually impaired people.

@@

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device. The suggested system integrates well with the main blind person's aid - the white cane. The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation, object/face recognition, obstacle detection, navigation). On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.

%Such a problem partially may be solved in near future, when 5G networks will prevail.

@@

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issule 4,  pp. 275-286, 2015.
%\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.
\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.
\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

@@

@@

>>>>

More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Larisa}. Such systems often lack convenience and brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). %This paper describes a high level architecture of the proposed technology aid for visually impaired people %(kartojasi su In this article we describe a system, which employs modern computer vision ...)

@@

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. The suggested system also integrates well with the main blind person's aid - the white cane. The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation, object/face recognition, obstacle detection, etc.). On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.

@@

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.

\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issule 4,  pp. 275-286, 2015.

@@

\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.

\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.

\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.

@@

\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.

\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
